Introduction - Illustrative example

### 2025-05-24 supplementary/examples-case-studies/1-Introduction/illustrative-example.Rmd
swithing to new branch

We use [data](example-data-2.csv) from a hypothetical experiment that evaluates the time performance of three user interface techniques (*A*, *B*, and *C*) that help users complete image editing tasks of four different difficulty levels: *Level1*, *Level2*, *Level3*, and *Level4*.

@@

We read our dataset and fix the type of the factors:
```{r, warning=FALSE}
df <- read.csv("example-data-2.csv", sep=",", header=TRUE, strip.white=TRUE)

@@

p1 <- (df %>%  group_by(Participant,Technique) %>% 
summarise(Time = median(Time), .groups="drop") %>%   
        ggplot(aes(x = Technique, y = Time, fill = Technique)) + 
        geom_boxplot(outlier.shape = NA) +
        ylab("Median Time (min)") +
        ylim(0, 8) + 
        geom_jitter(shape=20, position=position_jitter(0.1)) +
        theme_bw() + theme(legend.position = "none")) + scale_fill_manual(values=cbPalette)

p2 <- (df %>%  group_by(Participant,Difficulty,Technique) %>% 
           summarise(Time = median(Time), .groups="drop") %>%   
        ggplot(aes(x = Difficulty, y = Time, fill = Technique)) + 
        geom_boxplot(outlier.shape = NA) +
        ylab("Median Time (min)") +
        ylim(0, 10) +
        geom_point(size = 0.7, position=position_jitterdodge(0.1)) +
        theme_bw() + theme(legend.position = "none")) +
        scale_fill_manual(values=cbPalette)

@@

mpar <- lmer(Time ~ Difficulty*Technique + (1|Participant), data=df) # Parametric - no transformation
mlog <- lmer(log(Time) ~ Difficulty*Technique + (1|Participant), data=df) # Parametric - Log-transformation
mart <- art(Time ~ Difficulty*Technique + (1|Participant), data=df) # ARTool
mrnk <- lmer(rank(Time) ~ Difficulty*Technique + (1|Participant), data=df) # Rank transformation 
mint <- lmer(int(Time) ~ Difficulty*Technique + (1|Participant), data=df) # Inverse Transform transformation

model1 <- glmer(Time ~ Difficulty*Technique + (1|Participant), family = gaussian(link = "log"), data = df)
model2 <- glmer(log(Time) ~ Difficulty*Technique + (1|Participant), family = gaussian(link = "identity"), data = df)

```

>>>>

We use [data](example-data.csv) from a hypothetical experiment that evaluates the time performance of three user interface techniques (*A*, *B*, and *C*) that help users complete image editing tasks of four different difficulty levels: *Level1*, *Level2*, *Level3*, and *Level4*.

@@

We read our dataset and fix the type of the factors:
```{r, warning=FALSE}
df <- read.csv("example-data-cut.csv", sep=",", header=TRUE, strip.white=TRUE)

@@

p1 <- (df %>%  group_by(Participant,Technique) %>% 
summarise(Time = median(Time), .groups="drop") %>%   
        ggplot(aes(x = Technique, y = Time, fill = Technique)) + 
        geom_boxplot(outlier.shape = NA) +
        ylab("Median Time (min)") +
        ylim(0, 3) + 
        geom_jitter(shape=20, position=position_jitter(0.1)) +
        theme_bw() + theme(legend.position = "none")) + scale_fill_manual(values=cbPalette)

p2 <- (df %>%  group_by(Participant,Difficulty,Technique) %>% 
           summarise(Time = median(Time), .groups="drop") %>%   
        ggplot(aes(x = Difficulty, y = Time, fill = Technique)) + 
        geom_boxplot(outlier.shape = NA) +
        ylab("Median Time (min)") +
        ylim(0, 6) +
        geom_point(size = 0.7, position=position_jitterdodge(0.1)) +
        theme_bw() + theme(legend.position = "none")) +
        scale_fill_manual(values=cbPalette)

@@

mpar <- lmer(Time ~ Difficulty*Technique + (1|Participant), data=df) # Parametric - no transformation
mlog <- lmer(log(Time) ~ Difficulty*Technique + (1|Participant), data=df) # Parametric - Log-transformation
mart <- art(Time ~ Difficulty*Technique + (1|Participant), data=df) # ARTool
mrnk <- lmer(rank(Time) ~ Difficulty*Technique + (1|Participant), data=df) # Rank transformation 
mint <- lmer(int(Time) ~ Difficulty*Technique + (1|Participant), data=df) # Inverse Transform transformation
```
